### 2021-07-01 paper_v2/legacy/app_deprc.tex
paper revisions per chat

>>>>

\subsection{Re-estimation of McDonald (2004)}

\citet{mcdonald:2004} studies whether trade promotes peace between nations. \citet[p. 547]{mcdonald:2004} introduced the argument that free trade between states ``makes conflict less likely because of its efficiency over conquest in acquiring resources\ldots''. Accordingly, he provided evidence challenging the generalized linkage between peace and trade and refined the measurement of the standard ``trade'' variable, arguing that \textit{free} trade, rather than trade alone, reduces the likelihood of conflict between states. His key hypothesis is that greater levels of protection increase the probability of interstate conflict, an argument that builds on the work of classic liberalism and connects free trade to the power of domestic audiences. \citet{mcdonald:2004} measured free trade in two ways. The first, the ``protection'' variable measures the proportion of customs revenue divided by total imports in the state that possesses the greater such ratio in each dyad; this reflects the notion that larger protected sectors generate greater societal pressures resulting in pockets of support for war. This measure thus captures the score of the state in the dyad that possesses higher barriers to trade. \citet[p. 560]{mcdonald:2004} also includes a measure of economic integration  calculated as ``the lower proportion of total dyadic trade (imports plus exports) divided by state $i$'s GDP or total dyadic trade divided by state $j$'s GDP''. The (binary) dependent variable is the onset of a new militarized interstate dispute within a given dyad, and \citet{mcdonald:2004} includes splines to correct for temporal dependence with robust standard errors clustered on each dyad.
